Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-08-28 src/tex/ms.tex
minor text change

In \ref{fig:posterior_MPV}, we show the posterior on $M_{\rm PV}^{-1}$ for each event in our analysis.
Compared to Fig.~I in \citet{Zhu:2023wci}, we can see that the posteriors on some events are different between our analysis and theirs.
For example, the posterior for GW190727\_060333 peaks at zero in our analysis, but peaks at a nonzero value in \citet{Zhu:2023wci}.
This shows that the difference in the combined constraint may come from the difference in the individual event analyses.
However, we could not compare the analysis in \citet{Zhu:2023wci} with ours in detail, as their analysis result is not publicly available.

\begin{figure}
    \script{posterior_MPV.py}
    \includegraphics[width=\columnwidth]{figures/posterior_MPV.pdf}
    \caption{
        Individual-event $M_\mathrm{PV}^{-1}$ posteriors from our analysis, converted from the $\kappa$ posteriors in Fig.~\ref{fig:violin_kappa}.
        Chosen events are those labeled in Fig.~I of \citet{Zhu:2023wci}.
    }
    \label{fig:posterior_MPV}
\end{figure}

>>>>

In \ref{fig:posterior_MPV}, we show the posterior on $M_{\rm PV}^{-1}$ for each event in our analysis.
Compared to Fig.~1 in \citet{Zhu:2023wci}, we can see that the posteriors on some events are different between our analysis and theirs.
For example, the posterior for GW190727\_060333 peaks at zero in our analysis, but peaks at a nonzero value in \citet{Zhu:2023wci}.
This shows that the difference in the combined constraint may come from the difference in the individual event analyses.
However, we could not compare the analysis in \citet{Zhu:2023wci} with ours in detail, as their analysis result is not publicly available.

\begin{figure}
    \script{posterior_MPV.py}
    \includegraphics[width=\columnwidth]{figures/posterior_MPV.pdf}
    \caption{
        Individual-event $M_\mathrm{PV}^{-1}$ posteriors from our analysis, converted from the $\kappa$ posteriors in Fig.~\ref{fig:violin_kappa}.
        Chosen events are those labeled in Fig.~1 of \citet{Zhu:2023wci}.
    }
    \label{fig:posterior_MPV}
\end{figure}
